---
title: "bpmn - BPMN diagrams in R"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 9, fig.height = 3.5)
```

R package [bpmn](https://github.com/bergant/bpmn) is an interface to the [bpmn-js](https://github.com/bpmn-io/bpmn-js) JavaScript library (a BPMN 2.0 rendering toolkit and web modeler) from [bpmn.io](https://bpmn.io/) - a "Web-based tooling for BPMN, DMN and CMMN diagrams".
 
Using JavaScript in R is handled by [htmlwidgets](https://github.com/ramnathv/htmlwidgets) package. 


## Install 
Install R package (and required java script libraries) from GitHub:

```{r, eval=FALSE}
devtools::install_github("bergant/bpmn")
```


## Display a BPMN diagram

```{r}
library(bpmn)
```


Use `bpmn` widget with a BPMN file:

```{r}
bpmn_file <- system.file("examples/qr-code.bpmn", package = "bpmn")
bpmn(bpmn_file)
```


## Overlays

We can add additional notes (or any html element) aside any element of the 
diagram.

```{r }
overlays <- list(
  
  overlay(
    element = "SCAN_OK", 
    html = "<div style='color: red'>Mixed up the labels?</div>"
  ),
  overlay(
    element = "sid-52EB1772-F36E-433E-8F5B-D5DFD26E6F26", 
    html = "<div style='color: red'>Manually?</div>",
    top = -40,
    left = -40
  )
)

bpmn(bpmn_file, overlays = overlays)
```

## Elements in the diagram

Extract elements from BPMN with `bpmn_get_elements`:

```{r}

library(xml2)

htmlTable::htmlTable(align = "lll",
  bpmn_get_elements(
    read_xml(bpmn_file)
  )
)
```

## More

There are a lot of bpmn-js features (e.g. designing a new diagram) which are not 
yet supported by this widget. Expore these on bpmn.io [demo site](http://demo.bpmn.io/).


## Project

GitHub: https://github.com/bergant/bpmn

Issues: https://github.com/bergant/bpmn/issues


## Licenses

bpmn package: MIT License

See [license file](../inst/htmlwidgets/lib/bpmn-js/LICENSE) for 
the included **bpmn-js** library
